---
title: "Introduction to Data Science - Homework"
author: "Mike Powell mpowell3434@floridapoly.edu`"
output: html_notebook
---


# Problem 1 

Load the `tidyverse` package

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```

> In this problem you will work with vehicle fuel economy data from the US EPA (Environmental Protection Agency), ranging from 1985-2015. 

Read the data using the code below:

```{r, message=FALSE, warning=FALSE}
vehicles <- read_csv("https://raw.githubusercontent.com/reisanar/datasets/master/vehicles.csv")

vehicles
```

   Variable  | Description
-------------|-----------------------------------------
`id`         | Unique EPA identifier
`make`       | Manufacturer
`model`      | Model name
`year`       | Model year
`class`      | EPA vehicle size class
`trans`      | Transmission
`drive`      | Drive train
`cyl`        | Number of cylinders
`displ`      | Engine displacement, in litres
`fuel`       | Fuel type
`hwy`        | Highway fuel economy, in mpg
`cty`        | City fuel economy, in mpg


(a) (6 points) **Select** the different manufacturers (makes) of the cars in this data set. Save this vector in a variable called `makes`

```{r}
# Solution for 1A:

makes <- select(vehicles, make)


```


(b) (6 points) Can you determine **how many different car manufacturers** are represented by the data set?

```{r}
# Solution for 1B:

#distinct()  works as well

makes %>% 
  group_by(make) %>% 
  summarise(count = n()) %>% 
  nrow()

```


(c) (6 points) **Filter** the data set for vehicles manufactured in 1998.

```{r}
# Solution for 1C:

filter(vehicles, year == 1998)

```


(d) (6 points) **Mutate** the 1998 cars data frame to add a column `average` that has the average gas mileage (between city and highway MPG) for each car

```{r}
# Solution for 1D:

avg <- filter(vehicles, year == 1998) %>% 
  mutate(
       avg = (cty + hwy)/2)

avg

```


(e) (6 points) Of all vehicles, what is the vehicle ID of the vehicle with the worst highway MPG?

# worst milage look at e and f filter and select

```{r}
# Solution for 1E:

filter(vehicles, 
         hwy <= min(hwy)) %>% 
select(id, make)

```


(f) (6 points) Which 2013 Acura model has the best highway MPG? Which 2015 Honda model has the best highway MPG?

```{r}
# Solution for 1F:

filter(vehicles, year == 2013, make == "Acura" ) %>% 
filter(hwy >= max(hwy)) %>% 
select(id, make)


filter(vehicles, year == 2015, make == "Honda" ) %>% 
filter(hwy >= max(hwy)) %>% 
select(id, make)
```


(g) (6 points) Create a **data visualization** of your choice using this dataset. Comment on the results.

```{r}
# Solution for 1G:

ggplot(vehicles, mapping = aes(x = fuel, y = mean(hwy), color = fuel)) + 
  geom_bar(stat="identity") +
  coord_flip()

```


# Problem 2

Load the `nycflights13` package. 

```{r}
library(nycflights13)

flights
```


> Use the `flights` dataframe to answer the following questions. 

(a) (6 points) Find all flights headed to MCO, and **select** only the origin, destination, and the departure time.

```{r}
# Solution for 2A:

flights %>% 
  filter(dest == "MCO") %>% 
  select(origin, dest,  dep_time)


```


(b) (6 points) Consider flights from JFK to TPA. What was the **average, minimum, and maximum** _air time_ of those flights? 

```{r}
# Solution for 2B:

flights %>% 
  filter(origin == "JFK", dest == "TPA") %>% 
  
summarise(avg_air_time = mean(air_time, na.rm = T), 
          min_air_time = min(air_time, na.rm = T),
          max_air_time = max(air_time, na.rm = T))
```


(c) (6 points) What was the **average departure delay** in each month? Save this as a data frame `dep_delay_by_month`. (Hint: you may have to perform a grouping operation then summarizing your data).

```{r}
# Solution for 2C:

dep_delay_by_month <- flights %>% 
  group_by(month) %>% 
  summarise(avg_dep_delay = mean(dep_delay, na.rm = T))
dep_delay_by_month

```


(d) (8 points) Which month had the **largest average departure delay**?

```{r}
# Solution for 2D:

dep_delay_by_month %>% 
  arrange(-avg_dep_delay)

```


(e) (8 points) To which destinations were the **average arrival delays the highest**?

```{r}
# Solution for 2E:

highest_avg_arr_delay <- flights %>% 
  group_by(dest) %>% 
  summarise(
    avg_arr_delays = mean(arr_delay, na.rm = T)) %>% 
      arrange(-avg_arr_delays)

highest_avg_arr_delay
  

```


(f) (6 points) Which airline had the **smallest average arrival delay**?

```{r}
# Solution for 2F:

smallest_avg_arr_delay <- flights %>% 
  group_by(dest) %>% 
  summarise(
    avg_arr_delays = mean(arr_delay, na.rm = T)) %>% 
      arrange(avg_arr_delays)

smallest_avg_arr_delay

```


(g) (6 points) Find all flights that were operated by United, American, or Delta.

```{r}
# Solution for 2G:
condensed_flights <- flights %>% 
  filter(carrier == c("UA", "AA", "DL", na.rm = T))

condensed_flights
 

```


(h) (6 points) Find all the flights (if any) headed to Orlando, Tampa, or Miami with a scheduled departure time later than 8:00 PM.

```{r}
# Solution for 2H:

flights %>% 
  filter(dest == c("MCO", "TPA", "MIA", na.rm = T)) %>% 
           filter(dep_time >= 800)

```


(i) (6 points) Create a **data visualization** of your choice using this dataset. Comment on the results.

```{r}
# Solution for 2I:

condensed_flights %>% 
  ggplot(mapping = aes(x = carrier, y = air_time, color = dest, shape = carrier, na.rm = T)) +
geom_boxplot() +
  geom_line(aes(group = carrier)) 

```






