---
title: "Introduction to Data Science - HW 3"
author: "First Name Last name - `flastname@floridapoly.edu`"
output: html_notebook
---


# Problem 1 (20 Points)

Create the following vectors in `R` (see the pattern and use appropriate functions to construct these vectors):

$a = (5, 10, 15, 20, ..., 160)$

$b = (87, 86, 85, ..., 56)$

(a) (5 points) Multiply these vectors and call the result `d`. 

```{r}
# Solution for 1A:


```

(b) (5 points) What are the 19th, 20th, and 21st elements of `d`?

```{r}
# Solution for 1B:


```

(c) (5 points) What are all of the elements of `d` which are less than 2000?

```{r}
# Solution for 1C:


```


(d) (5 points) How many elements of `d` are greater than 6000?

```{r}
# Solution for 1D:


```


# Problem 2 (20 Points)

Start with this vector of `nouns`.  

```{r}
nouns <- c("apple", "flower", "insect", "lettuce", "knife", "dog", "cloud", "person", "cabinet", "flower" )
```

(a) (5 points) Use the `length()` function to display the number of elements in `nouns`.

```{r}
# Solution for 2A:


```

(b) (5 points) Use indexing to create a new vector consisting of the first 4 elements of `nouns`.

```{r}
# Solution for 2B:


```

(c) (5 points) Use indexing to create a new vector consisting of only the last 8 elements of `nouns`.

```{r}
# Solution for 2C:


```

(d) (5 points) Use indexing to create a new vector of the 1st, 3rd through 6th, and 10th elements of `nouns` (the length of the resulting vector should be 6).

```{r}
# Solution for 2D:


```


# Problem 3 (30 Points)

(a) (5 points) Create a vector `my_breakfast` of everything you ate for breakfast.

```{r}
# Solution for 3A:


```

(b) (5 points) Create a vector `my_lunch` of everything you ate (or will eat) for lunch.

```{r}
# Solution for 3B:


```

(c) (5 points) Create a list `meals` that contains your breakfast and lunch.

```{r}
# Solution for 3C:


```

(d) (5 points) Add a "dinner" element to your `meals` list that has what you plan to eat for dinner.

```{r}
# Solution for 3D:


```

(e) (5 points) Use dollar notation to extract your `dinner` element from your list and save it in a vector called 'dinner'.

```{r}
# Solution for 3E:


```

(f) (5 points) Use double-bracket notation to extract your `lunch` element from your list and save it in your list as the element at index 5 (no reason beyond practice).

```{r}
# Solution for 3F:


```


# Problem 4 (30 Points)

(a) (5 points) Create a vector of the number of points the Chicago Bulls (NBA team) scored in the most recent 4 games of the season (Google "Chicago Bulls" for the scores!)

```{r}
# Solution for 4A:


```

(b) (5 points) Create a vector of the number of points the Bulls have allowed to be scored against them in each of the first 4 games of the season.

```{r}
# Solution for 4B:


```

(c) (5 points) Combine your two vectors into a dataframe called `games`.

```{r}
# Solution for 4C:


```

(d) (5 points) Create a new column "diff" that is the difference in points between the teams. Hint: recall the syntax for assigning new elements (which in this case will be a vector) to a list!

```{r}
# Solution for 4D:


```

(e) (5 points) Create a new column "won" which is `TRUE` if the Bulls won the game.

```{r}
# Solution for 4E:


```

(f) (5 points) Create a vector of the opponent names corresponding to the games played and add it to your dataframe.

```{r}
# Solution for 4F:


```

