---
title: "Working with Data Frames"
output: html_notebook
---

  
# Exercise 1: creating data frames



Create a vector of the number of points the Orlando Magic scored in the last 4 January games of the season (Google "Orlando Magic" for the scores!)

```{r}
# example from 2019 - 20 season

points <- c(92, 97, 98, 114)

```



Create a vector of the number of points the Orlando Magic have allowed to be scored against them in each of the last 4 January games of the season

```{r}

points_allowed <- c(113, 112, 109, 120)

```

Combine your two vectors into a data frame called `games`

```{r}
# hw problem
games <- data.frame(points, points_allowed)

```

```{r}

#head lets you see your data
head(games)
dim(games)
```
```{r}

# practice
games$points
```


Create a new column `gap` that is the difference in points between the teams (recall the syntax for assigning new elements (which in this case will be a vector) to a list!


```{r}
#
games[["gap"]] <- games$points - games$points_allowed

```

Create a new column "won" which is TRUE if the Orlando Magic won the game

```{r}
games$won <- games$points > games$points_allowed
```

Check the current data frame `games`

```{r}
games
```


Create a vector of the opponent names corresponding to the games above

```{r}
opponents <- c("Miami Heat", "La Clippers", "Boston Celtics", "OKC Thunder")
```

Add a column to the `games` data frame with the names of the opponents

```{r}
games$opponents <- opponents

```

Check the final version of the data frame

```{r}
games
```


# Working with built-in data sets


Load R's `USPersonalExpenditure` dataset using the `data()` function. 

```{r}
data('USPersonalExpenditure')
```

```{r}
USPersonalExpenditure
```
```{r}
is.data.frame(USPersonalExpenditure)

class(USPersonalExpenditure)
```


Check the object using the `head()` function

```{r}

```

Is the object `USPersonalExpenditure` a data frame? Use `is.data.frame()` to check 

```{r}

```

Create a new object called `us_exp` that is a data frame version of the `USPersonalExpenditure` object

```{r}

us_exp <- as.data.frame(USPersonalExpenditure)

```

Do we have a data frame now?

```{r}
is.data.frame(us_exp)

```

What are the column names?

```{r}
colnames(us_exp)
```

Notice anything? Are there "row names" for `us_exp`?

```{r}
rownames(us_exp)
```

Add a column `category` to your data frame that contains the row names

```{r}

us_exp$catagory <- row.names(us_exp)
us_exp
```

Check again

```{r}

```

How much money was spent on Food and Tobacco in 1960?

```{r}
us_exp[1, 5]

us_exp["Food and Tobacco", "1960"]

```

